Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-28 chapters/introduction/introduction.tex
in location and orientation

  \item \textbf{Constraint for Time and Coarse Location:}
  In this work, we estimate the probability over the
  capture time and the camera geographic location given the input image.
  Our network has two branches which predict the image
  capture time and the geographic location simultaneously.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the UTC hour of the
  day when the input image has been captured.
  For coarse camera geo-localization, We provide two approaches to
  obtain the probability distribution over the camera geographic
  location. Most straightforwardly, our network outputs the discrete
  distribution over the geographic location of the camera. Better
  results can be procured with the image capture time as auxiliary input
  (if it is known).  We present the algorithm details in
  \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating the geo-orientation of the camera. 
  We trained our network with cross-view pairs.
  We first learn to deduce the semantic layout of the ground
  scene from the associated aerial image.
  Given a geographic location and orientation, we sample the aerial
  image, then compare its semantic layout of the ground scene
  with the semantic layout of the query image (ground image).
  We assign a score to that location and orientation by matching these
  two semantic layouts.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

>>>>

  \item \textbf{Constraint for Time and Location:}
  In this work, we estimate the probability over the
  capture time and the camera geographic location given the input image.
  Our network has two branches which predict the image
  capture time and the geographic location simultaneously.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the UTC hour of the
  day when the input image has been captured.
  For coarse camera geo-localization, We provide two approaches to
  obtain the probability distribution over the camera geographic
  location. Most straightforwardly, our network outputs the discrete
  distribution over the geographic location of the camera. Better
  results can be procured with the image capture time as auxiliary input
  (if it is known).  We present the algorithm details in
  \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the discrete camera location. The predictions are only approximate
  due to the limitation of the algorithm. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation with overhead imagery.
%
  We first learn to deduce the semantic layout of the ground
  scene from the associated aerial image.
  Given a geographic location and orientation, we sample the aerial
  image, then compare its semantic layout of the ground scene
  with the semantic layout of the query image (ground image).
  We assign a score to that location and orientation by matching these
  two semantic layouts.
  We present the algorithm details in \chapref{crosstransf}.
  \newline
